An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-17 main.tex
Rephrase sentence about the removed strategies.

This manuscript provides a detailed numerical analysis of agent-based simulations
of \textbf{\input{./tex/num_strategies.tex}}complex and adaptive strategies for the
IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
effort to provide software for reproducible research for the IPD\@. The library
now contains over \input{./tex/num_strategies_axelrod.tex}parameterized
strategies including classics like TitForTat and WinStayLoseShift, as well as
recent variants such as OmegaTFT, zero determinant and other memory one
strategies, strategies based on finite state machines, lookup tables, neural
networks, and other machine learning based strategies, and a collection of novel
strategies. Not all strategies have been considered for this study: excluded
are those that make use of knowledge of the game such as the number of turns
and others that have a high
computational run time. The large number of strategies are available thanks to
the open source nature of the project with over 40 contributors from around the
world, made by programmers and researchers \cite{Knight2016}. Three of the considered
strategies are finite state machines trained specifically for Moran processes
(described further in Section~\ref{sec:strategies}.

>>>>

This manuscript provides a detailed numerical analysis of agent-based simulations
of \textbf{\input{./tex/num_strategies.tex}}complex and adaptive strategies for the
IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
effort to provide software for reproducible research for the IPD\@. The library
now contains over \input{./tex/num_strategies_axelrod.tex}parameterized
strategies including classics like TitForTat and WinStayLoseShift, as well as
recent variants such as OmegaTFT, zero determinant and other memory one
strategies, strategies based on finite state machines, lookup tables, neural
networks, and other machine learning based strategies, and a collection of novel
strategies. Not all strategies have been considered for this study: excluded
are those that make use of knowledge of the number of turns in a match
and others that have a high
computational run time. The large number of strategies are available thanks to
the open source nature of the project with over 40 contributors from around the
world, made by programmers and researchers \cite{Knight2016}. Three of the considered
strategies are finite state machines trained specifically for Moran processes
(described further in Section~\ref{sec:strategies}.
